2016 Brussels Bombings

### 2019-05-25 report/report.Rmd
Plot plan routes in separate layer of leaflet interactive map
Add missing delay info from EBBR

```{r, fig.align='center'}
ddr.jsmap(data$real$routes[id %in% div[, id]], div, coord)
```

@@

```{r, results='asis'}
for (icao in nearby) {
	cat(paste('-', icao, 'delays:\n\t- Departures:\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & (date >= event[1] & date <= event[2]), mean(depdel)] - delays[airport == icao & date < event[1], mean(depdel)]) / delays[airport == icao & date < event[1], mean(depdel)] * 100), '%'), 'while', bru, 'was closed with respect to before the attack\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & date > event[2], mean(depdel)] - delays[airport == icao & date < event[1], mean(depdel)]) / delays[airport == icao & date < event[1], mean(depdel)] * 100), '%'), 'after', bru, 'reopens with respect to before the attack\n\t- Arrivals:\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & (date >= event[1] & date <= event[2]), mean(arrdel)] - delays[airport == icao & date < event[1], mean(arrdel)]) / delays[airport == icao & date < event[1], mean(arrdel)] * 100), '%'), 'while', bru, 'was closed with respect to before the attack\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & date > event[2], mean(arrdel)] - delays[airport == icao & date < event[1], mean(arrdel)]) / delays[airport == icao & date < event[1], mean(arrdel)] * 100), '%'), 'after', bru, 'reopens with respect to before the attack\n'))
}
```

>>>>

```{r, fig.align='center'}
ddr.jsmap(data$real$routes[id %in% div[, id]], div, coord, data$plan$routes[id %in% div[, id]])
```

@@

```{r, results='asis'}
for (icao in c(bru, nearby)) {
	cat(paste('-', icao, 'delays:\n\t- Departures:\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & (date >= event[1] & date <= event[2]), mean(depdel)] - delays[airport == icao & date < event[1], mean(depdel)]) / delays[airport == icao & date < event[1], mean(depdel)] * 100), '%'), 'while', bru, 'was closed with respect to before the attack\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & date > event[2], mean(depdel)] - delays[airport == icao & date < event[1], mean(depdel)]) / delays[airport == icao & date < event[1], mean(depdel)] * 100), '%'), 'after', bru, 'reopens with respect to before the attack\n\t- Arrivals:\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & (date >= event[1] & date <= event[2]), mean(arrdel)] - delays[airport == icao & date < event[1], mean(arrdel)]) / delays[airport == icao & date < event[1], mean(arrdel)] * 100), '%'), 'while', bru, 'was closed with respect to before the attack\n\t\t*', paste0(sprintf('%+.1f', (delays[airport == icao & date > event[2], mean(arrdel)] - delays[airport == icao & date < event[1], mean(arrdel)]) / delays[airport == icao & date < event[1], mean(arrdel)] * 100), '%'), 'after', bru, 'reopens with respect to before the attack\n'))
}
```
